A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-09-30 paper.tex
Final Updates
Missing abstract keywords
Final Updates
Image Labels update

@@

Many of the publications with the most influence on our research
~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
propose a cloud-native optimization architecture that features population-based
algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
which planted the seed of thought of our current paper.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig1}
    \end{figure}

@@

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown in Figure~\ref{fig2}. The general
flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig4}.

\begin{figure}
    \centering
    \includegraphics[width=70mm]{img/fig2_proposal.pdf}
    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig2}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
    \caption{Newton's Law of Universal Gravitation.} \label{fig3}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
    \caption{Life-Cycle algorithm general flowchart.} \label{fig4}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig5}
    \end{figure}

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (Closed
Reproduction process), and couple match by creating a new mating individual
(Open Reproduction process). We use many combinations of the containerized
processes, up to the minimum number required to obtain good results.
Figure~\ref{fig5} shows a comparison of only two alternatives for the
implementation of the algorithm. Our experimentation started with a
configuration of ten processes and ended in five, shown on the left and right
sides of Fig.~\ref{fig5}, respectively.

>>>>

%\keywords{Distributed Bioinspired Algorithms \and Genetic Algorithms \and Cloud Computing.}

@@

Many of the publications with the most influence on our research
~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
propose a cloud-native optimization architecture that features population-based
algorithms. They present ideas such as those mentioned in Figure~\ref{fig.background},
which planted the seed of thought of our current paper.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig.background}
    \end{figure}

@@

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown in Figure~\ref{fig.proposal}. The general
flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig.flowchart}.

\begin{figure}
    \centering
    \includegraphics[width=70mm]{img/fig2_proposal.pdf}
    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig.proposal}
    \end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
    \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
    \caption{Newton's Law of Universal Gravitation.} \label{fig.newtonslaw}
    \end{figure}

@@

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig.processes_containers}
    \end{figure}

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (Closed
Reproduction process), and couple match by creating a new mating individual
(Open Reproduction process). We use many combinations of the containerized
processes, up to the minimum number required to obtain good results.
Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the
implementation of the algorithm. Our experimentation started with a
configuration of ten processes and ended in five, shown on the left and right
sides of Fig.~\ref{fig.processes_containers}, respectively.
